---
title: "ATP Dataset"
output:
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r}
library(flexdashboard)
library(wordcloud)
library(RColorBrewer)
library(wordcloud2)
library(janitor)
library(openxlsx)
library(tidyverse)
library(plotly)
library(ggmap)
library(prob)
library(sampling)
library(data.table)
library(dplyr)
library(ggplot2)
library(readr)
library(ggthemes)
library(magrittr)
library(dplyr)
library(jsonlite)
library(maptools)
library(leaflet)



#Reading regional files

atp <- read.csv(file.choose(),header = T) ## ## Please choose the written csv file ATP, name of the file is ATP

match_level <- c("G","M","F")

atp1 <- atp[atp$tourney_level %in% match_level,]

atp2 <- atp1[atp1$tourney_date > 19910000,]

atp3 <- atp2[atp2$round == "F",]

atp4 <- atp3[ , -which(names(atp3) %in% c("winner_entry","loser_entry"))]

atp4$minutes[atp4$minutes == ""] <- 190

atp4$w_ace[atp4$w_ace == ""] <- 0
atp4$w_df[atp4$w_df == ""] <- 0
atp4$w_bpSaved[atp4$w_bpSaved == ""] <- 0
atp4$w_bpFaced[atp4$w_bpFaced == ""] <- 0
atp4$l_ace[atp4$l_ace == ""] <- 0
atp4$l_df[atp4$l_df == ""] <- 0
atp4$l_bpSaved[atp4$l_bpSaved == ""] <- 0
atp4$l_bpFaced[atp4$l_bpFaced == ""] <- 0

write.csv(atp4,"C:\\Users\\gtiwa\\OneDrive\\Documents\\R\\ATPDATASET1.csv", row.names = FALSE)

atpdatset <- read.csv(file.choose(),header = T)## Please choose the written csv file ATPDATASET1, name of the file is ATPDATASET1


```

### Number of winners per copuntry

```{r}
k<-atpdatset %>%
  distinct(winner_name, winner_ioc) %>%
  group_by(winner_ioc) %>%
  summarize("Distinct players of a country" = n())
#k

data <- data.frame(k)

data$winner_ioc <- factor(data$winner_ioc, levels = unique(data$winner_ioc)[order(data$Distinct.players.of.a.country, decreasing = TRUE)])


plot_ly(data, x = ~data$winner_ioc, y = ~data$Distinct.players.of.a.country, type = 'bar', color = ~data$winner_ioc,
        hoverinfo = 'text',
        hovertext = ~paste0(data$Distinct.players.of.a.country, ' ', data$winner_ioc))%>% layout(title = "Distinct Winners as per country",
        xaxis = list(title = "Country"),yaxis = list(title = "Number of distinct winners"))


```
### What is the distribution of aces by the different type of surfaces?

```{r}
acesnetfinals <- rowSums(atpdatset[, c("w_ace", "l_ace")])
#acesnetfinals
data <- data.frame(atpdatset$surface, atpdatset$w_ace, atpdatset$l_ace, acesnetfinals)
#data

plot_ly(data, x = ~data$atpdatset.surface, y = ~data$acesnetfinals, type = 'box', color = ~data$atpdatset.surface,
        hoverinfo = 'text',
        hovertext = ~paste0(data$acesnetfinals, ' ', data$atpdatset.surface))%>% layout(title = "Distribution of aces as per surface",
        xaxis = list(title = "Type of surface"),yaxis = list(title = "Total no. of aces in final"))


```

### Serving Stats
```{r}

k1<-atpdatset %>%
  distinct(w_ace, winner_name) %>%
  group_by(winner_name) %>%
  summarize("Most number of aces in finals" = n())

k2<-atpdatset %>%
  distinct(w_df, winner_name) %>%
  group_by(winner_name) %>%
  summarize("Most number of df in finals" = n())

k3<-atpdatset %>%
  distinct(w_bpSaved, winner_name) %>%
  group_by(winner_name) %>%
  summarize("Most number of bp saved in finals" = n())

k4<-atpdatset %>%
  distinct(w_bpFaced, winner_name) %>%
  group_by(winner_name) %>%
  summarize("Most number of bp faced in finals" = n())

data1 <- data.frame(k1,k1$`Most number of aces in finals` ,k2$`Most number of df in finals`, k3$`Most number of bp saved in finals`, k4$`Most number of bp faced in finals`)

library(plotly)



p1 <- plot_ly(data1, x = ~data1$winner_name, y = ~data1$k2..Most.number.of.df.in.finals.) %>%
  add_lines(name = ~"Most Number of Double Faults in the finals")%>% layout(
                                                                            xaxis = list(title = "Tournament Winners"),yaxis = list(title = "values",range(0,20)))
p2 <- plot_ly(data1, x = ~data1$winner_name, y = ~data1$k3..Most.number.of.bp.saved.in.finals.) %>%
  add_lines(name = ~"Most number of BP saved in the finals")%>% layout(
                                                                       xaxis = list(title = "Tournament Winners"),yaxis = list(title = "values",range(0,20)))
p3 <- plot_ly(data1, x = ~data1$winner_name, y = ~data1$k4..Most.number.of.bp.faced.in.finals.) %>%
  add_lines(name = ~"Most number of BP faced in the finals")%>% layout(
                                                                       xaxis = list(title = "Tournament Winners"),yaxis = list(title = "values",range(0,20)))
p4 <- plot_ly(data1, x = ~data1$winner_name, y = ~data1$Most.number.of.aces.in.finals) %>%
  add_lines(name = ~"Most number of aces in the finals")%>% layout(
                                                                   xaxis = list(title = "Tournament Winners"),yaxis = list(title = "values",range(0,20)))
p <- subplot(p1, p2, p3, p4, nrows = 2, shareX = TRUE, shareY =TRUE)%>%layout(title = 'Serving Stats of the Winners of ATP tournament')
annotations = list( 
  list(x= 0.2, y = 1,text = "Number of Double Faults in the finals",xref = "paper", yref = "paper",  xanchor = "center",  yanchor = "bottom", showarrow = FALSE ),list(x= 0.8, y = 1,text = "Number of bp saved",xref = "paper", yref = "paper",  xanchor = "center",  yanchor = "bottom", showarrow = FALSE ),list(x= 0.2, y = 0.45,text = "Number of bp faced",xref = "paper", yref = "paper",  xanchor = "center",  yanchor = "bottom", showarrow = FALSE ),list(x= 0.8, y = 0.45,text = "Number of aces",xref = "paper", yref = "paper",  xanchor = "center",  yanchor = "bottom", showarrow = FALSE )
)
p <- p%>%layout(annotations = annotations)
p

```


### Distribution of winner aces based on winner's hand as per the surface

```{r}
library(ggplot2)

dfwa <- atpdatset %>% group_by(winner_hand,surface)%>% summarise(totalacesperhandpersurface = sum(w_ace))


dfwb <- atpdatset %>% group_by(winner_hand)%>% summarise(totalacesperhand = sum(w_ace))


dfdat <- left_join(dfwa, dfwb)


dfdat$perc <- dfdat$totalacesperhandpersurface/dfdat$totalacesperhand * 100


plot_ly(x = dfdat$winner_hand, y = dfdat$perc, color = dfdat$surface, text=c(dfdat$totalacesperhandpersurface),textposition = 'auto',hoverinfo = 'text') %>%
  add_bars() %>%
  layout(barmode = "stack")%>% layout(title = "Number of aces hit by surfaces as per their style of play",
                                      xaxis = list(title = "Style of play()Left handed vs Right handed"),yaxis = list(title = "Distribution of aces as per surface in percentage", ticksuffix ="%"))




```

### Tournaments played on each court

```{r}
library(ggplot2)
library(readr)
library(ggthemes)
library(dplyr)

k1<- atpdatset %>% count(atpdatset$surface)

k1$`atpdatset$surface` <- factor(k1$`atpdatset$surface`, levels = unique(k1$`atpdatset$surface`)[order(k1$n, decreasing = TRUE)])

plot_ly(x = k1$`atpdatset$surface`,
        y = k1$n, type = "bar", color = k1$`atpdatset$surface`, colors = "Dark2")%>% layout(title = " Number of Tournaments played as per surface",
                                                                                            xaxis = list(title = "Surface"),yaxis = list(title = "Total number of matches played"))


```

### Scatter Plot between Winners height and winners ace

```{r}
p11 <- plot_ly(type = "scatter",
               x = ~atpdatset$winner_ht,
               y = ~atpdatset$w_ace,
               mode = "markers",
               marker = list(size = (10)
                            )) %>% 
  layout(title = "Winners Height vs total ace hit in the finals",
         xaxis = list(title = "Winner Height"),
         yaxis = list(title = "Winners Ace"))

p11

```

### Players with most tournament wins in the given period

```{r}
library(dplyr)
total_wins <- atpdatset %>% group_by(winner_name)%>%
  summarize(total_wins = n())%>%
  arrange(desc(total_wins))

top_10_df <-  head(total_wins, n=10)
#top_10_df

top_10_df$winner_name <- factor(top_10_df$winner_name, levels = unique(top_10_df$winner_name)[order(top_10_df$total_wins, decreasing = TRUE)])

top10 <- plot_ly(x = top_10_df$winner_name,
              y = top_10_df$total_wins,
              color = top_10_df$winner_name,
              colors = "Dark2",
              type = "bar") %>%layout(xaxis = list(dtick = 1))%>% layout(title = "Number of Tournament won by different Tournament Winners",
                                                                         xaxis = list(title = "Tournament Winners"),yaxis = list(title = "Tournament won"))
top10



```
### Summary of the winners rank at the time of tournament win countrywise

```{r}
p8 <- plot_ly(data = atpdatset,x = ~winner_ioc,
              y = ~winner_rank,
              color = ~winner_ioc,
              colors = "Dark2",
              type = "box")%>% layout(title = "Summary of the winners rank at the time of tournament win countrywise",
                                      xaxis = list(title = "Country"),yaxis = list(title = "Summary of Rank", range = c(0,60)))
p8



```
### Winners Break point with age distribution as per surface

```{r}
library(ggplot2)
library(ggthemes)
library(data.table)
#head(atpdatset)
atp1sub <- atpdatset[c("winner_age","w_bpSaved","surface")]
#head(atp1sub)
#pl <- ggplot(atp1sub,aes(x=winner_age,y=w_bpSaved,color=surface)) + geom_point(size=3,shape=1)
#pl

pl1 <- plot_ly(data= atp1sub, x=atp1sub$winner_age, y= atp1sub$w_bpSaved, color = atp1sub$surface,colors = "Dark2", type   = 'scatter', 
               mode   = 'markers',
               marker = list(size = atp1sub$w_bpSaved*3),opacity = 0.6,symbol = atp1sub$surface, symbols = c('circle','x','o','square'))%>% layout(title = "Distribution of breakpoint saved as per age of the winners",
                                                                                     xaxis = list(title = "Age of the winners"),yaxis = list(title = "bp_saved"))
pl1

```

### Distribution of Winner's age of the countries having more than 10 wins

```{r}
datacountry <- names(which(table(atpdatset$winner_ioc) > 10))
wins15country <- subset(atpdatset, winner_ioc %in% datacountry)


#=========================================
#Main dataset for distribution of wins
#DISTRIBUTION THROUGH HISTOGRAM
#=========================================

library(plotly)


#Wins distribution of USA by age
mysubset <- subset(wins15country, winner_ioc %in% "USA")
#table(round(mysubset$winner_age, 0))
o <- round(mysubset$winner_age, 0)
#hist(o, ylim = c(0, 30), breaks = seq(15, 39, 3), xaxp=c(15, 39, 8), main = "Winners age distribution of USA by age", xlab = "Ages", ylab = "No. of winners", col="Light Blue")
graph1 <- plot_ly(x = o, type = "histogram", marker= list(color="E45756"), name = "Winners age distribution of USA by age")%>%layout(xaxis = list(title = 'Winner Age'), yaxis = list(title = 'NO. of Wins',range=c(0,40)))
#graph1

#Wins distribution of SPAIN by age
mysubset <- subset(wins15country, winner_ioc %in% "ESP")
#table(round(mysubset$winner_age, 0))
o <- round(mysubset$winner_age, 0)
#hist(o, ylim = c(0, 30), breaks = seq(15, 39, 3), xaxp=c(15, 39, 8), main = "Winners age distribution of Spain by age", xlab = "Ages", ylab = "No. of winners", col="Yellow")
graph2 <- plot_ly(x = o, type = "histogram", marker= list(color="Blue"), name = "Winners age distribution of Spain by age")%>%layout(xaxis = list(title = 'Winner Age'), yaxis = list(title = 'NO. of Wins',range=c(0,40)))
#graph2

#Wins distribution of UNITED KINGDOM by age
mysubset <- subset(wins15country, winner_ioc %in% "GBR")
#table(round(mysubset$winner_age, 0))
o <- round(mysubset$winner_age, 0)
#hist(o, ylim = c(0, 10), breaks = seq(15, 39, 3), xaxp=c(15, 39, 8), main = "Winners age distribution of United Kingdom by age", xlab = "Ages", ylab = "No. of winners", col="Grey")
graph3 <- plot_ly(x = o, type = "histogram", marker= list(color="Green"), name = "Winners age distribution of UK by age")%>%layout(xaxis = list(title = 'Winner Age'), yaxis = list(title = 'NO. of Wins',range=c(0,40)))
#graph3

#Wins distribution of SWITZERLAND by age
mysubset <- subset(wins15country, winner_ioc %in% "SUI")
#table(round(mysubset$winner_age, 0))
o <- round(mysubset$winner_age, 0)
#hist(o, ylim = c(0, 20), breaks = seq(15, 39, 3), xaxp=c(15, 39, 8), main = "Winners age distribution of Switzerland by age", xlab = "Ages", ylab = "No. of winners", col="Red")
graph4 <- plot_ly(x = o, type = "histogram", marker= list(color="Yellow"), name = "Winners age distribution of Switzerland by age")%>%layout(xaxis = list(title = 'Winner Age'), yaxis = list(title = 'NO. of Wins',range=c(0,40)))
#graph4

#Wins distribution of SERBIA by age
mysubset <- subset(wins15country, winner_ioc %in% "SRB")
#table(round(mysubset$winner_age, 0))
o <- round(mysubset$winner_age, 0)
#hist(o, ylim = c(0, 20), breaks = seq(15, 39, 3), xaxp=c(15, 39, 8), main = "Winners age distribution of Serbia by age", xlab = "Ages", ylab = "No. of winners", col="Orange")
graph5 <- plot_ly(x = o, type = "histogram", marker= list(color="Orange"), name = "Winners age distribution of Serbia by age")%>%layout(xaxis = list(title = 'Winner Age'), yaxis = list(title = 'NO. of Wins',range=c(0,40)))
#graph5

o <- round(wins15country$winner_age, 0)
graph6 <- plot_ly(x = o, type = "histogram", marker= list(color="Lime"), name = "Winners age distribution of five countries by age")%>%layout(xaxis = list(title = 'Winner Age'), yaxis = list(title = 'NO. of Wins',range=c(0,40)))
#hist(o, ylim = c(0, 100), breaks = seq(15, 39, 3), xaxp=c(15, 39, 8), main = "Winners age distribution of five countries by age", xlab = "Ages", ylab = "No. of winners", col="Light Blue")


finalgraph <- subplot(graph1, graph2, graph3, graph4, graph5,graph6, nrows = 3, shareY = TRUE, shareX = TRUE) %>% 
  layout(title = "Winners age Distribution of Countries by Age", xaxis = list(title = 'Winners age '), yaxis = list(title = 'NO. of Wins'))
finalgraph

```
### Distribution of winners age countrywise

```{r}
plot_ly(data = wins15country, y = wins15country$winner_age,x = wins15country$winner_ioc, type = "box", color = wins15country$winner_ioc)%>% layout(title= "Distribution of age of the winners of the Countries with
                                                                                                                                                   most title during the period", xaxis = list(title = 'Countries'), yaxis = list(title = 'Ages'))



```

### Central Limit Theorem
```{r}

sample23 <- 250

xbar31 = numeric(250)
xbar32 = numeric(250)
xbar33 = numeric(250)
xbar34 = numeric(250)
for (i in 1:250) {
  xbar31[i] <- mean(sample(atpdatset$minutes, 
                           size = 10, replace = TRUE))
}
minutes.data1 <- data.frame(xbar31)
#minutes.data1
p1 <- plot_ly(minutes.data1, x= ~minutes.data1$xbar31, type = 'histogram',histnorm = 'probability', name = "Sample size = 10")%>%
  layout(xaxis = list(title = 'xbar',range=c(0,200)), yaxis = list(title = 'density',range=c(0,0.2)))

for (i in 1:250) {
  xbar32[i] <- mean(sample(atpdatset$minutes, 
                           size = 20, replace = TRUE))
}
minutes.data2 <- data.frame(xbar32)
p2 <- plot_ly(minutes.data2, x= ~minutes.data2$xbar32, type = 'histogram',histnorm = 'probability', name = "Sample size = 20")%>%
  layout(xaxis = list(title = 'xbar',range=c(0,200)), yaxis = list(title = 'density',range=c(0,0.2)))


for (i in 1:250) {
  xbar33[i] <- mean(sample(atpdatset$minutes, 
                           size = 30, replace = TRUE))
}
minutes.data3 <- data.frame(xbar33)
p3 <- plot_ly(minutes.data3, x= ~minutes.data3$xbar33, type = 'histogram',histnorm = 'probability',name = "Sample size = 30")%>%
  layout(xaxis = list(title = 'xbar',range=c(0,200)), yaxis = list(title = 'density',range=c(0,0.2)))


for (i in 1:250) {
  xbar34[i] <- mean(sample(atpdatset$minutes, 
                           size = 40, replace = TRUE))
}
minutes.data4 <- data.frame(xbar34)
p4 <- plot_ly(minutes.data4, x= ~minutes.data4$xbar34, type = 'histogram',histnorm = 'probability',name = "Sample size = 40")%>%
  layout(xaxis = list(title = 'xbar',range=c(0,200)), yaxis = list(title = 'density',range=c(0,0.2)))


p <- subplot(p1, p2, p3, p4, nrows = 2, shareY = TRUE, shareX = TRUE)%>%layout(title = 'Central Limit Theorem')
annotations = list( 
  list(x= 0.2, y = 1,text = "Sample Size =10",xref = "paper", yref = "paper",  xanchor = "center",  yanchor = "bottom", showarrow = FALSE ),list(x= 0.8, y = 1,text = "Sample Size =20",xref = "paper", yref = "paper",  xanchor = "center",  yanchor = "bottom", showarrow = FALSE ),list(x= 0.2, y = 0.45,text = "Sample Size =30",xref = "paper", yref = "paper",  xanchor = "center",  yanchor = "bottom", showarrow = FALSE ),list(x= 0.8, y = 0.45,text = "Sample Size =40",xref = "paper", yref = "paper",  xanchor = "center",  yanchor = "bottom", showarrow = FALSE )
  )
p <- p%>%layout(annotations = annotations) 

p


```

### Simple random sampling for atpdataset for Minutes attriubutes and number of aces by the winner

```{r}
#names(atpdatset)
#nrow(atpdatset)

#table(atpdatset$winner_ioc)

m1 <- mean(atpdatset$w_ace)
m2 <- mean(atpdatset$minutes)
sd1 <- sd(atpdatset$minutes)
sd2 <- sd(atpdatset$w_ace)

c1 <- paste("Mean=",m1,"Sd=",sd1)
c2 <- paste("Mean=",m2,"Sd=",sd2)

s1 <- plot_ly(atpdatset, x= ~atpdatset$minutes, type = 'histogram',histnorm = 'probability', name = "Population  Distribution for match duration")%>%
  layout(xaxis = list(title = 'Distribution of Match Duration'), yaxis = list(title = 'Frequency',range=c(0,0.40)))
s2 <- plot_ly(atpdatset, x= ~atpdatset$w_ace, type = 'histogram',histnorm = 'probability', name = " Population Distribution for Winners ace")%>%
  layout(xaxis = list(title = 'Distribution of Winners Aces'), yaxis = list(title = 'Frequency',range=c(0,0.40)))

s <- srswr(70,nrow(atpdatset))
#s[s!=0]
rows <- (1:nrow(atpdatset))[s!=0]
rows <- rep(rows, s[s!=0])
#rows
sample.1 <- atpdatset[rows,]

#table(sample.1$winner_ioc)

m3<- mean(sample.1$w_ace)
m4<-mean(sample.1$minutes)
sd3<-sd(sample.1$minutes)
sd4<-sd(sample.1$w_ace)

c3 <- paste("Mean=",m3,"Sd=",sd3)
c4 <- paste("Mean=",m4,"Sd=",sd4)
s3 <- plot_ly(sample.1, x= ~sample.1$minutes, type = 'histogram', histnorm = 'probability',name = "Sample  Distribution for match duration")%>%
  layout(xaxis = list(title = 'Distribution of Match Duration'), yaxis = list(title = 'Frequency',range=c(0,0.40)))

s4 <- plot_ly(sample.1, x= ~sample.1$w_ace, type = 'histogram',histnorm = 'probability', name = "Sample  Distribution for Winners aces")%>%
  layout(xaxis = list(title = 'Distribution of Winner Aces'), yaxis = list(title = 'Frequency',range=c(0,0.40)))

s <- subplot(s1, s2, s3, s4, nrows = 2, shareX = TRUE,shareY = TRUE)%>%layout(title = 'Simple random Sampling')
annotations = list( 
  list(x= 0.2, y = 1,text = paste("Population",c2),xref = "paper", yref = "paper",  xanchor = "center",  yanchor = "bottom", showarrow = FALSE ),list(x= 0.8, y = 1,text = paste("Population",c1),xref = "paper", yref = "paper",  xanchor = "center",  yanchor = "bottom", showarrow = FALSE ),list(x= 0.2, y = 0.45,text = paste("Sample",c4) ,xref = "paper", yref = "paper",  xanchor = "center",  yanchor = "bottom", showarrow = FALSE ),list(x= 0.8, y = 0.45,text = paste("Sample",c3),xref = "paper", yref = "paper",  xanchor = "center",  yanchor = "bottom", showarrow = FALSE )
)
s <- s%>%layout(annotations = annotations) 
s
```

### Systematic Sampling
```{r}
set.seed(2692)

m5<-mean(atpdatset$w_ace)
m6<-mean(atpdatset$minutes)
sd6<-sd(atpdatset$minutes)
sd5<-sd(atpdatset$w_ace)

c5 <- paste("Mean=",m5,"Sd=",sd5)
c6 <- paste("Mean=",m6,"Sd=",sd6)

ssa <- plot_ly(atpdatset, x= ~atpdatset$minutes, type = 'histogram',histnorm = 'probability',name = "Population Distribution for match duration")%>%
  layout(xaxis = list(title = 'Distribution of Match Duration'), yaxis = list(title = 'Frequency',range=c(0,0.5)))
ssb <- plot_ly(atpdatset, x= ~atpdatset$w_ace, type = 'histogram',histnorm = 'probability',name = "Population Distribution for Winners aces")%>%
  layout(xaxis = list(title = 'Distribution of Winners Aces'), yaxis = list(title = 'Frequency',range=c(0,0.5)))
N <- nrow(atpdatset)
n1 <- 40



k1 <- ceiling(N/n1)


r1 <- sample(k1,1)

ss1 <- seq(r1,by = k1, length = n1)
#ss1

sample.2 <- atpdatset[ss1,]
#sample.2
#table(sample.2$winner_ioc)
m7<-mean(sample.2$w_ace,na.rm=TRUE)
#m7
m8<-mean(sample.2$minutes,na.rm=TRUE)
sd8<-sd(sample.2$minutes,na.rm=TRUE)
sd7<-sd(sample.2$w_ace,na.rm=TRUE)

c7 <- paste("Mean=",m7,"Sd=",sd7)
c8 <- paste("Mean=",m8,"Sd=",sd8)

ssc <- plot_ly(sample.2, x= ~sample.2$minutes, type = 'histogram', histnorm = 'probability',name = "Sample Distribution for match duration")%>%
  layout(xaxis = list(title = 'Distribution of Match Duration'), yaxis = list(title = 'Frequency',range=c(0,0.50)))
ssd <- plot_ly(sample.2, x= ~sample.2$w_ace, type = 'histogram',histnorm = 'probability',name = "Sample Distribution for Winners aces")%>%
  layout(xaxis = list(title = 'Distribution of Winners Aces'), yaxis = list(title = 'Frequency',range=c(0,0.50)))

ss <- subplot(ssa, ssb, ssc, ssd, nrows = 2, shareX = TRUE,shareY = TRUE)%>%layout(title = 'Systematic Sampling')
annotations = list( 
  list(x= 0.2, y = 1,text = paste("Population",c6),xref = "paper", yref = "paper",  xanchor = "center",  yanchor = "bottom", showarrow = FALSE ),list(x= 0.8, y = 1,text = paste("Population",c5),xref = "paper", yref = "paper",  xanchor = "center",  yanchor = "bottom", showarrow = FALSE ),list(x= 0.2, y = 0.45,text = paste("Sample",c8) ,xref = "paper", yref = "paper",  xanchor = "center",  yanchor = "bottom", showarrow = FALSE ),list(x= 0.8, y = 0.45,text = paste("Sample",c7),xref = "paper", yref = "paper",  xanchor = "center",  yanchor = "bottom", showarrow = FALSE )
)
ss <- ss%>%layout(annotations = annotations) 
ss
```

### Stratified sampling
```{r}
set.seed(2692)

strs1<- table(atpdatset$winner_ioc)
#strs1

strso <- strs1[order(strs1, decreasing = TRUE)]
#strso

top4 <- head(strso, 4)
#top4 

top5names <- names(top4)
#top5names



subset1 <- atpdatset[atpdatset$winner_ioc %in% top5names,]
#subset1


mst1 <- mean(subset1$minutes)
sdst1 <- sd(subset1$minutes)
mst2 <- mean(subset1$w_ace)
sdst2<- sd(subset1$w_ace)

cst1 <- paste("Mean  of subset_winners ace=",mst1,"Sd of subset_winners ace=",sdst1)
cst2 <- paste("Mean of subset_duration of match=",mst2,"Sd of subset_duration of match=",sdst2)

freq1 <- table(subset1$winner_ioc)
#freq1
st.sizes <- round(8* freq1/sum(freq1))
#st.sizes
#st.sizes[st.sizes!=0]
st.1 <- strata(subset1, stratanames = c("winner_ioc"), size = rep(2,4), method = "srswor", description = TRUE)

st1.sample4 <- getdata(subset1, st.1)



mst3<-mean(st1.sample4$minutes)
sdst3<-sd(st1.sample4$minutes)

mst4<-mean(st1.sample4$w_ace)
sdst4<-sd(st1.sample4$w_ace)

cst3 <- paste("Mean of strata 1_duration of minutes=",mst3,"Sd of strata 1_duration of minutes=",sdst3)
cst4 <- paste("Mean of strata 1_winners ace=",mst4,"Sd  of strata 1_winners ace=",sdst4)

cat("\n",cst1,"\n",cst4,"\n",cst2,"\n",cst3)

```

### Percentage of Breakpoints saved against the Breakpoints faced of the players having tournament wins more than 7

```{r}
library(tidyverse)
df <- atpdatset

df <- as_tibble(df)

dfbp <- df %>%group_by(winner_name) %>% summarise(bp_faced = sum(w_bpFaced), bp_saved = sum(w_bpSaved), tournament_won = n())%>%dplyr::filter(tournament_won>7)%>%
  mutate(Perc_bp_saved = (bp_saved/bp_faced * 100))  %>%
  select(winner_name,tournament_won, bp_saved, bp_faced,Perc_bp_saved )%>% arrange(desc(Perc_bp_saved))%>%head(10)

dfbp$winner_name <- factor(dfbp$winner_name, levels = unique(dfbp$winner_name)[order(dfbp$Perc_bp_saved, decreasing = TRUE)])

fig <- dfbp %>% plot_ly()
fig <- fig %>% add_trace(x = ~dfbp$winner_name, y = ~dfbp$bp_saved, type = 'bar',
                         text = (dfbp$bp_saved), textposition = 'auto',hovertext = dfbp$Perc_bp_saved,
                         marker = list(color = 'rgb(158,202,225)',
                                       line = list(color = 'rgb(8,48,107)', width = 1.5)),name = "Breakpoints saved")
fig <- fig %>% add_trace(x = ~dfbp$winner_name, y = ~dfbp$bp_faced, type = 'bar',
                         text = dfbp$bp_faced, textposition = 'auto',hovertext = dfbp$Perc_bp_saved,
                         marker = list(color = 'rgb(58,200,225)',
                                       line = list(color = 'rgb(8,48,107)', width = 1.5)),name = "Breakpoints faced")

fig <- fig %>% layout(title = "Percentage of BP saved by players",
                      barmode = 'group',
                      xaxis = list(title = ""),
                      yaxis = list(title = ""))



fig
```

### Wordcloud

```{r, message=FALSE, warning=FALSE}

dfd <- atpdatset

dfd <- as_tibble(dfd)

dfdp <- dfd %>%group_by(winner_name) %>% summarise(tournament_won = n())

set.seed(2312)

wordcloud(words = dfdp$winner_name, freq = dfdp$tournament_won, min.freq = 1, max.words=200, random.order=FALSE, rot.per=0.35,colors=brewer.pal(8, "Dark2"),scale=c(3.5,0.25))

```